%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based on: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
%\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Paul Walko} \\ \vspace{1pt}
    \small +1 (502) 509-6242 $|$ \href{mailto:paul@bigcavemaps.com}{paul@bigcavemaps.com} $|$ 
    \href{https://paul.walko.org}{paul.walko.org} $|$
    \href{https://git.seaturtle.pw/pew}{git.seaturtle.pw/pew} $|$ \href{https://github.com/paulwalko}{github.com/paulwalko}
\end{center}





%-----------EMPLOYMENT-----------
\section{Employment}
  \resumeSubHeadingListStart
    \resumeSubheading
      {DevOps Engineer} {Aug. 2019 -- Present}
      {Ozmo, Inc}{Blacksburg, VA}
      \resumeItemListStart
	    \resumeItem{\textbf{Observability}: Built monitoring stack with Grafana, OpenTelemetry, ELK, Kafka}
      	\resumeItem{\textbf{AWS ECS/Fargate}: Helped migrate from Elasticbeanstalk}
      	\resumeItem{\textbf{SOC 2}: Key component of SOC 2 Audit process}
        \resumeItem{\textbf{CI Testing}: Significantly improved PR turnaround time and developer happiness with automated testing}
        \resumeItem{\textbf{OpenVPN Cloud}: Implemented always on split-tunnel VPN to support remote work}
        \resumeItem{Helped build event-driven search service in AWS: \\ \href{https://ozmo.com/blog/building-a-world-wide-real-time-search-service/}{https://ozmo.com/blog/building-a-world-wide-real-time-search-service/}}
      \resumeItemListEnd

    \resumeSubheading
      {Systems Engineer }{Jan. -- July 2019}
      {Solers, Inc}{Arlington, VA}
      \resumeItemListStart
        \resumeItem{Worked with Docker Swarm and Ansible}
        \resumeItem{Deployed central logging solution for clustered environment}
      \resumeItemListEnd

    \resumeSubheading
      {Research Assistant - Analyzed Netflow data} {Sep. 2016 -- Dec. 2017}
      {Hume Center at Virginia Tech}{Blacksburg, VA}
      \resumeItemListStart
        \resumeItem{Learned about issues with large data sets}
        \resumeItem{Intercepted data from keyboards, mice, and other BLE devices}
        \resumeItem{Created Bluetooth pen-testing device with Ubertooth One and worked with devs on IRC}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \small{\item{\textbf{GitHub}{: \href{https://github.com/paulwalko}{github.com/paulwalko}}
      \textbf{Gitea}{: \href{https://git.seaturtle.pw/pew}{git.seaturtle.pw/pew}}}}
      
      \resumeProjectHeading
      	{\textbf{Self-Hosted Services}}{}
      	\resumeItemListStart
      	
      	  \resumeItem{\textbf{Mergin Maps}{: \href{https://maps.caving.dev}{maps.caving.dev.} Used on remote caving expeditions to manage GIS.}}
      	  
      	  \resumeItem{\textbf{Mastodon}{: \href{https://social.bigcavemaps.com}{social.bigcavemaps.com}}}
      	  
      	  \resumeItem{\textbf{Geoserver/Leaflet/MapProxy}:{ Used to analyze lidar and find potential caves.}}
      	  
      	  \resumeItem{\textbf{Cavepedia}: \href{https://git.seaturtle.pw/pew/cavepedia}{git.seaturtle.pw/pew/cavepedia}. Architected pipeline to import old document, perform OCR, analyze readability, and index into a fully offline searchable application for use in the field.}
      	  
      	  \resumeItem{\textbf{Minio, Gitea, Photoview}}
      	\resumeItemListEnd
      		     
      \resumeProjectHeading
        {\textbf{Free/Open Software Contributions}}{}
        \resumeItemListStart
        \resumeItem{\textbf{2013 -- Present}{: Use and contribute to OpenStreetMap, especially not well known trails. \href{https://www.openstreetmap.org/user/bigmapscaver}{openstreetmap.org/user/bigmapscaver}.}}
          \resumeItem{\textbf{2019 -- Present}{: \href{https://archiveteam.org/}{Archive Team}: Help archive Internet services and manage massive amounts of data.}}
        \resumeItemListEnd
    \resumeSubHeadingListEnd
    
%-----------ORGANIZATIONS-----------
\section{Organizations}
	\resumeSubHeadingListStart
	      \resumeSubheading
	      {\textbf{VPI Cave Club} $|$ \emph{\href{https://vpicave.club}{vpicave.club}}}{2020 - Present}{Student Grotto of the National Speleological Society (NSS)}{}

	\resumeItemListStart
	\resumeItem{\textbf{Survey/Cartography}{: Survey and map unexplored cave passage, including data entry and processing to create a finished map.}}
	\resumeItem{\textbf{Training}{: Teach new members basic caving skills, including vertical competence when climbing or abseiling rope.}}
	\resumeItem{\textbf{Events}{: Help organize regional caving events with 200+ attendees.}}
	\resumeItemListEnd

\resumeProjectHeading
{\textbf{Virginia Tech Linux/Unix Users Group (VTLUUG)} $|$ \emph{\href{https://vtluug.org/}{vtluug.org}, \href{https://github.com/vtluug}{github.com/vtluug}}} {2016 - Present}
\resumeItemListStart
\resumeItem{\textbf{FreeIPA/LDAP}{: Maintain accounts for email, shell access, and webserver.}}
\resumeItem{\textbf{\href{https://vtluug.org/wiki/Infrastructure}{Rebuilt Infrastructure}}{: Updated services to deploy with Ansible and run all services with Docker.}}
\resumeItem{\textbf{Organized funds}{: Obtained \$1300 for new servers and equipment; oversaw purchasing additional components.}}
\resumeItemListEnd
	
      \resumeProjectHeading
{\textbf{Outdoor Club at Virginia Tech (OCVT)} $|$ \emph{\href{https://ocvt.club/}{ocvt.club}, \href{https://github.com/ocvt}{github.com/ocvt}}} {2017 - Present}
\resumeItemListStart
\resumeItem{\textbf{\href{https://github.com/ocvt/dolabra}{Dolabra}}{: Built backend API in Golang and SQLite + front-end in plain HTML/JavaScript. Used Open-ID Connect for auth, Stripe for payments, and Docker for testing and deployment in AWS.}}
\resumeItem{\textbf{Appalachian Trail Maintenance}{: Regularly clear trail of trees, brush, and clean shelters.}}
\resumeItemListEnd

      \resumeProjectHeading
{\textbf{Amateur Radio} $|$ Callsign: KN4VDC} {2019 - Present}
	\resumeSubHeadingListEnd
	
	
	
%-----------TALKS-----------
\section{Talks}
\resumeSubHeadingListStart
\small{\item{
		\textbf{Cave Rescue Communications }{ (Toorcamp 2024)}: \href{https://archive.is/iX4s8}{https://archive.is/iX4s8} \\
		\textbf{Austrian Expedition to the Loser Plateau}{ (NSS Convention 2023)} \\
		\textbf{Newberry's Cave Exploration}{ (NSS Convention 2022)} \\
}}
\resumeSubHeadingListEnd
    
%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Virginia Tech}{Blacksburg, VA}
{Bachelor of Science in Computer Science; Minor in Cyber Security} {Aug. 2015 -- Dec. 2018}
\small{\item{
		\textbf{AWS}{: API Gateway, CloudFormation, CloudFront, CloudWatch, EC2, ECS/Fargate, ElasticSearch/OpenSearch, Lambda, RDS, Route53, RDS, S3} \\
		\textbf{GIS Tools}{: QGIS, GDAL, Leaflet, GeoServer, MapProxy} \\
		\textbf{Languages}{: Bash, C, Java, JavaScript/NodeJS, Python, Ruby} \\
		\textbf{Tools}{: Docker, Google Workspace, Git, Grafana, Jenkins, Librato, Linux, NewRelic, Ubiquiti} \\
}}
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}